\documentclass[11pt]{letter}
\usepackage[letterpaper, margin=1in]{geometry}
\usepackage{hyperref}
\usepackage{setspace}

\date{October 30, 2025}

\begin{document}

% Custom header block (left aligned)
\begin{flushleft}
\textbf{Eric Ni} \\
Toronto, ON \\
647-545-9818 \\
\href{mailto:eric.ni@mail.utoronto.ca}{eric.ni@mail.utoronto.ca} \\
\vspace{1em}
October 30, 2025
\end{flushleft}

\vspace{2em}

% Recipient
\begin{flushleft}
EA SPORTS \\
Vancouver, BC
\end{flushleft}

\vspace{1.5em}

\noindent Dear EA Hiring Team,

\vspace{1em}

I am writing to apply for the \textbf{Software Developer Intern} position at EA SPORTS. As a University of Toronto Computer Science student with experience in Node.js, React, and TypeScript, I am excited by the opportunity to contribute to EA's web ecosystem and learn from your world-class development team.

My technical background aligns directly with your stack. I have built full-stack applications using Next.js and React, including \textit{CoverSume}, where I developed a dynamic interface with JavaScript and integrated REST APIs. My experience with component-based architecture and responsive design through projects like my personal portfolio has prepared me to contribute to your design system and Storybook component library. At MarkiTech.AI, I worked with Node.js and Express to build a scalable website for clinics, and I containerized the backend using Docker for deployment. I am familiar with Git workflows and have collaborated in Agile environments as a Scrum Master, giving me practical experience with sprint planning and code reviews.

I am particularly drawn to EA's focus on creating next-level entertainment experiences and would be thrilled to apply my full-stack skills to support EA's global community of players. The opportunity to gain exposure to CMS integration, performance optimization, and production deployment processes represents an ideal environment for my growth as a developer.

Thank you for considering my application. I have attached my resume and welcome the opportunity to discuss how my experience with modern web technologies can contribute to EA's innovative projects.

\vspace{1.5em}
\noindent Sincerely,\\[0.5em]
\noindent Eric Ni

\end{document}
