\documentclass[11pt]{letter}
\usepackage[letterpaper, margin=1in]{geometry}
\usepackage{hyperref}
\usepackage{setspace}

\date{October 30, 2025}

\begin{document}

% Custom header block (left aligned)
\begin{flushleft}
\textbf{Eric Ni} \\
Toronto, ON \\
647-545-9818 \\
\href{mailto:ericni2013@gmail.com}{ericni2013@gmail.com} \\
\href{https://www.linkedin.com/in/eric-ni-017985225/}{LinkedIn} \\
\href{https://github.com/ericnii}{GitHub} \\
\vspace{1em}
October 30, 2025
\end{flushleft}

\vspace{2em}

% Recipient
\begin{flushleft}
Applanix \\
Toronto, ON
\end{flushleft}

\vspace{1.5em}

\noindent Dear Hiring Manager,

\vspace{1em}

I am writing to express my interest in the \textbf{Software Engineering Intern} position at Applanix, as advertised. As a Computer Science student at the University of Toronto with a strong foundation in C/C++, Python, and web technologies, I am eager to contribute to your team and gain valuable experience in real-time firmware development.

My academic background and project experience align well with the requirements of this role. I have developed software solutions using C/C++ and Python, focusing on real-time systems and data analysis. For instance, during my internship at MarkiTech.AI, I utilized Node.js and Express to build scalable web applications, which honed my skills in software development and deployment. Additionally, my familiarity with HTML, CSS, and JavaScript complements my core programming skills, allowing me to contribute effectively to diverse projects.

I am particularly drawn to the opportunity to work on Trimble Applanix’s real-time APX/AP+ firmware. The chance to engage in debugging, data analysis, and algorithm implementation excites me, as does the prospect of using tools like GIT and JIRA in a professional setting. My experience in Agile environments and my role as a Scrum Master have equipped me with the ability to collaborate efficiently and manage multiple tasks.

I am enthusiastic about the possibility of joining Applanix and contributing to your innovative projects. Thank you for considering my application. I look forward to the opportunity to discuss how my skills and experiences align with the goals of your team.

\vspace{1.5em}
\noindent Sincerely,\\[0.5em]
\noindent Eric Ni

\end{document}