\documentclass[11pt]{letter}
\usepackage[letterpaper, margin=1in]{geometry}
\usepackage{hyperref}
\usepackage{setspace}

\date{\today}

\begin{document}

% Custom header block (left aligned)
\begin{flushleft}
\textbf{Eric Ni} \\
Toronto, ON \\
647-545-9818 \\
\href{mailto:ericni2013@gmail.com}{ericni2013@gmail.com} \\
\vspace{1em}
\today
\end{flushleft}

\vspace{2em}

% Recipient
\begin{flushleft}
Safuture \\
58 Mentor Boulevard
\end{flushleft}

\vspace{1.5em}

\noindent Dear Hiring Manager,

\vspace{1em}

I am writing to express my interest in the \textbf{Coding and Debugging} position at Safuture. With a strong background in software and web development, I am eager to contribute my skills in HTML, JavaScript, CSS, Node.js, and Angular to your team.

During my time at the University of Toronto, I gained extensive experience in developing full-stack applications. My proficiency in the Angular framework and familiarity with the MVC design model have equipped me to design and test robust computer structures. Additionally, my knowledge of Python and C\# for backend development, along with experience in Android Studio for mobile applications, aligns well with the requirements of this role.

I have a proven track record of managing database systems and maintaining operating systems, which will be beneficial for troubleshooting system errors and editing source-code. My experience in profiling and analyzing algorithms, as well as implementing build systems, will support Safuture's mission to deliver high-quality tech support.

I am particularly drawn to Safuture's innovative approach and would be thrilled to apply my skills to support your projects. I am confident that my strong communication and collaboration skills will make me a valuable asset to your team.

Thank you for considering my application. I have attached my resume and look forward to the opportunity to discuss how my experience can contribute to Safuture's success.

\vspace{1.5em}
\noindent Sincerely,\\[0.5em]
\noindent Eric Ni

\end{document}